---
title: "day-21"
subtitle: 'ESS 330'
author:
  - name: Nina Hayford
    email: "ninahayf@colostate.edu"
format: html
execute: 
  echo: true
---
## Load Libraries
```{r}
library(dataRetrieval)
library(dplyr)
library(tsibble)
library(ggplot2)
library(plotly)
library(feasts)
library(lubridate)
```

## Download and Prepare Data 
```{r}
poudre_flow <- readNWISdv(siteNumber = "06752260",
                          parameterCd = "00060",
                          startDate = "2013-01-01",
                          endDate = "2023-12-31") |>
  renameNWISColumns() |>
  mutate(Date = yearmonth(Date)) |>
  group_by(Date) |>
  summarise(Flow = mean(Flow, na.rm = TRUE))
```

## Convert to tsibble
```{r}
poudre_tsibble <- as_tsibble(poudre_flow, index = Date)
```

## Plot Time Series 
```{r}
gg_time <- ggplot(poudre_tsibble, aes(x = Date, y = Flow)) +
  geom_line(color = "blue") +
  labs(title = "Monthly Mean Streamflow: Cache la Poudre River",
       x = "Date", y = "Flow (cfs)")

gg_time
```
```{r}
# Animate with plotly
ggplotly(gg_time)
```

## Subseries Plot 
```{r}
gg_subseries(poudre_tsibble, Flow)
```
## Interpretation
The subseries plot shows how streamflow changes by month across years. Each line represents a year, and each facet represents a month, which helps visualize seasonal cycles. Typically, you'll notice higher flows in spring/early summer and lower flows in late summer/fall. The "subseries" are the flow values for each month across the years, showing consistent seasonal peaks and troughs. 

